An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
update application section

We shall map a database of research papers to an evolving graph $G_n$
in such a way that if author $i$ cited author $j$ on a paper published
at  time $t$, the evolving graph $G_n$ contains a directed edge from
$i$ to $j$ at time stamp $t$. Then given an author $a$ at time stamp $t_0$,
we can use our evolving-graph BFS to construct $T(a, t_0)$ which is
a set of all the authors that have been influenced by $a$'s work at
time $t_0$. We define a \emph{community} to be a group of
researchers that share the same information source.
For example, given a paper published by $a$ at year $2016$,
we can determine $a$'s community by first backward searching to
find the source then forward searching to find the descendants.

To design such system, we shall use two parameters:
 a parameter for
determining the layers of the backward search tree which can be chosen by the user;
a second parameter for determining the number of roots as a means of
filtering out unessential or overlapping trees. The subset of roots can be determined
by ranking algorithms like PageRank or machine-learning based preference ranking.

>>>>

We shall map a database of research papers to an evolving graph $G_n$
in such a way that if author $i$ cited author $j$ on a paper published
at  time $t$, the evolving graph $G_n$ contains a directed edge from
$i$ to $j$ at time stamp $t$. Then given an author $a$ at time stamp $t_0$,
we can use our evolving-graph BFS to construct $T(a, t_0)$ which is
a set of all the authors that have been influenced by $a$'s work at
time $t_0$. We define a \emph{community} to be a group of
researchers that have been influenced by the same authors.
For example, given a paper published by $a$ at year $2016$,
we can determine $a$'s community by first backward searching to
find the root authors then forward searching to find the descendants.

To design such information retrieval system, two parameters will be needed:
 one for determining the layers of the backward search tree which can be 
adjusted by the user;
the other for determining root authors for forward searching 
so that we can 
filter out unessential or overlapped trees, which can be computed
by ranking algorithms like PageRank \cite{pbmw99} or machine-learning based preference ranking.
